A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-04 paper/theor-experiment.tex
linda's second round of edits

To ensure that the optimizer works correctly we solved the benchmark
  problem (\ref{eqn:bench}).
To that end, we use a metric for comparing the quality of a Pareto
  front.
Given a point in the Pareto set, we compute the $m$ dimensional volume (for
  $m$ objectives) of the dominated space, relative a chosen origin.
We visualize this for $2$ objectives in Fig.~\ref{fig:hypervolume}.
For further information and details of the implementation see~\cite{whbb:12}.
Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
  Table~\ref{tbl:bench_rms_error}.
The reference Pareto front is clearly very well approximated.
It took a total of 1100 function evaluations to perform this computation.
The hypervolume of the reference solution ($0.6575$) for our benchmark was
  computed by sampling the solution provided in~\cite{hbwh:05}.

@@

@@

\subsection{AWA Photoinjector Optimization} \label{awaproblem}
Next we apply the optimization framework to a high charge beam line
 at the Argonne Wakefield Accelerator (AWA) facility. 
The goal of this optimization is to produce beams of electrons that meet 
design specifications; this includes number of particles (charge), energy, and particle distribution (characterized by beam sizes and energy spread).
As shown in Fig.~\ref{awa-linac}, the installed portion of the the 
beam line consists of an rf photocathode gun, 
two solenoids, and six linear accelerating cavities
followed by four quadrupoles and a stripline kicker. 
The charge of interest, 40 nC, is needed for Two Beam 
Acceleration (TBA) \cite{gai_power_jing_2012,JING201872} 
experiments performed at AWA, which motivates this work.

Prior experimental results were limited by beam size when the beam passed through small aperture 
wakefield structures located downstream. 
In an attempt to maximize charge transmission in upcoming experiments
we optimize magnet strengths in the gun and quadrupoles leading into the 
TBA section of the beam line, shown in Fig.~\ref{awa-tba}.
The simulation model includes the linac, kicker, and septum. 
The optimization location is chosen as the longitudinal 
entrance to the first quadrupole on the dog leg ($s_3$), see Fig.~\ref{awa-tba}.
Minimizing beam sizes here will enable capture and further focusing before space charge effects dominate the beam. 
This will also enable cleaner transport through downstream elements.
%\vspace{-1em}

@@

In addition to the physics challenges, we chose this model to demonstrate the ability of the framework to tackle large problems.
Six design variables and objectives were used, along with three constraints.
The objectives include transverse and longitudinal beam sizes, 
transverse momentum, and longitudinal energy spread. 
The design variables include the two gun solenoids and 
the first four quadrupoles. 
This problem encompasses high dimensionality 
and nonlinear effects such as space charge. There is no existing information
that accurately predicts optimized parameters for this beam line. 
This work is also meaningful in that it will guide future operations at the AWA.

\subsubsection{Time Step Scan} \label{awa:subsection:test}
Before running a full scale optimization of the problem described in Subsection \ref{awaproblem}, 
a study on time step and number of particles in the simulation model 
was done to reduce the time to simulation while 
maintaining the physics of interest. 
The grid size $16 \times 16 \times 32$ was chosen, 
and parallelized in the x and y directions.
After comparing several options (1,000, 10,000, 20,000, 50,000, 100,000) 
with a small time step, the number of particles was fixed at ten thousand.
Next several time steps were explored, see Table~\ref{timestep}.
The largest steps were too big to resolve the physics needed.
See low fidelity plot in Fig.~\ref{tstep} for $dT=$\num{5E-11} results.

\begin{table}%[h!]
	\begin{center}
		\caption{Checkmarks (\cmark) indicate desired physics is resolved at that time step. 
			An (\xmark) indicates the time step is too large, and results are nonphysical.}
		\label{timestep}
		\begin{tabular*}{0.48\textwidth}{c @{\extracolsep{\fill}} C c D }
			\hline\noalign{\smallskip}
			Time Step (dT) & Linac & Drift & Quadrupoles \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			$5 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$5 \times10^{-11}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-11}$  & \cmark & \cmark & \xmark \\
			$5 \times10^{-12}$  & \cmark & \cmark & \xmark \\
			$1 \times10^{-12}$  & \cmark & \cmark & \cmark \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

@@

The resulting simulations are low fidelity in most places, but closely approximate 
the mid fidelity simulations for metrics of interest, as shown in 
Fig.~\ref{tstep}.  Where we consider mid fidelity as a simulation of the 
beam line using $dT=\num{1E-12}$ everywhere. The
average run time of each simulation with the adjusted time steps was 1.6~minutes.
In comparison, the mid fidelity simulation ran for 18~minutes.
Note, a smaller time step, \num{1E-13}, is always used in the gun where the 
beam is low energy and changing rapidly.
%A summary of the parameters used is listed in Table \ref{fidelity}.

@@

The maximum number of individuals per generation was fixed at 80, 
Each experiment was allowed to run for twenty four hours, with 
a maximum generation limit of 100. 
We reduced the six objectives to four, 
and shortened the simulation time by moving the objectives further 
upstream to $s_1$ and $s_2$.
The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
\lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
The OPAL input file for ex-3 is given as an example to show how optimization and design variables are defined:
%

@@

After collection of the data for all four experiments, several metrics
were compared, including number of generations completed in twenty four hours and
Pareto fronts at $s_1$ and $s_2$.
From Table \ref{extable}, we clearly see ex-3 is significantly 
slower, as it evaluated only 53 generations compared to the max 
experiment, ex-1 at 96 generations.
Perhaps this trade off would be acceptable if the Pareto front was significantly 
improved, but from Fig. \ref{expareto}, we can see this is not the case.
Similar arguments can be made for ex-2, which evaluated about 15 less generations
with no clear benefit in either Pareto front.
The Pareto fronts at $s_1$, are nearly identical. We could expect
this trend would continue given more time. 
When looking at the Pareto front at $s_2$, only ex-4 has a slight 
edge over the others.
With ex-2 and ex-3 eliminated due to evaluation time, 
and a slightly better Pareto front at $s_2$ for ex-4, the hyper parameters in ex-4 were chosen as the default values for subsequent runs.

@@

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are calculated at 
$s_3=19.4$~m. See Fig.~\ref{awa-tba} for location of $s_3$ w.r.t. other 
beam line elements. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24 \, \text{or} \, 25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

The first four objectives, Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
at the location of interest in the beam line ($s_3$).
%Where $s_3$ is the longitudinal entrance of the fifth quadrupole. 
Minimizing the beam size at this location is essential to 
to preventing loss of particles by scraping; 
which ensures better transmission through the wakefield structures downstream. 
Less divergence in the beam (lower transverse momentum) 
reduces growth of transverse beam size after the focal point (min beam size).
This reduces halo by ensuring the beam is not over focused through a hard waist.
The momentum is also critical to preventing large growth during transport in bending elements. 
All of these factors help with transmission downstream.

The next two objectives in Eq. (\ref{eq:awa:p4}) minimize the 
longitudinal beam size ($rms_s$), and energy spread (dE) at location $s_3$.
This helps reduce longitudinal beam size growth in bending elements.
A small bunch length ($rms_s$) is also critical to the goals of 
TBA experiments. The power generated in the wakefield structures 
designed for TBA is related to the bunch length \cite{JING201872}.
\nrnote{need better source for this info} 
i.e. smaller bunch lengths result in larger wakefields and higher power generation.

Eqs.~\ref{eq:awa:c1} to \ref{eq:awa:c3} 
define three constraints used to guide the algorithm.
The bounding values may seem large, but this is done to avoid over constraining the 
problem in early generations. When the constraints were set tighter, 
optimization runs did not reach the second generation within a 48 hour time limit. 
In other words, enough satisfactory points were not produced to fill a complete generation in 48 hours. 
By leaving the value large, a sufficient number of simulations finish
and subsequent generations are reached in a timely manner. 
As multiple generations, the objectives continue to improve.

@@

Design variables include the currents in two gun solenoids (IBF and IM), 
and four quadrupole strengths (KQ1-KQ2). The objectives include
beam size (transverse and longitudinal), transverse momentum, and energy spread as
defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
The location at the entrance of the kicker is $s_1=16.45$~meters, 
and the location of interest for objectives is $s_3=19.4$~meters.

@@

Again, the location of optimization is $s_3=19.4$ [m]. 
This is the entrance to the fifth quad in the beam line. 
This location is where the beam should be captured and focused through subsequent elements.
After collection of the data, Pareto fronts comparing the objectives were plotted, 
see Figs.~\ref{fig:pareto1} and \ref{fig:pareto2}.

@@

As expected, the x dimension is impacted by the bending elements, and unable to reach 
the small beam sizes seen in the y dimension. This suggest objectives in the x 
dimension will drive design variable choices used in operations. 
However, it is still necessary to 
include the y dimension in optimization. Early optimization tests showed the y dimension 
can easily grow out of control if not included in the objectives.
Those results are not shown here due to the unfeasible solutions they resulted in
(i.e. $rms_y$ larger than the beam pipe).
In the case of bunch length, there are not many options to choose from.
Ignoring the extreme value on the right, Fig.~\ref{fig:pareto2} shows the 
range of optimal bunch lengths fall between 1.39 and 1.5 mm.

With these observations in mind, several beam parameters corresponding to
options on Pareto Front in Fig.~\ref{fig:pareto1} were plotted and compared. 
A select result is shown in Fig.~\ref{fig:stat}. 
The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat} (b).
The solution is nearly round, which will increase changes of keeping the beam nearly round
as it travels to the last triplet in Fig.~\ref{awa-tba}.
Overall this solution is satisfactory, and meets all requirements at the AWA.

>>>>

To ensure that the optimizer works correctly we solved the benchmark
  problem (\ref{eqn:bench}).
To that end, we use a metric for comparing the quality of a Pareto
  front.
Given a point in the Pareto set, we compute the $m$ dimensional volume (for
  $m$ objectives) of the dominated space, relative to a chosen origin.
We visualize this for $2$ objectives in Fig.~\ref{fig:hypervolume}.
For further information and details of the implementation see~\cite{whbb:12}.
\lsedit{The next sentence is confusing.  If hyper volumes referring to fig. 6, why is there only one value?  Is it an average?}
Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
  Table~\ref{tbl:bench_rms_error}.
The reference Pareto front is clearly very well approximated.
It took a total of 1100 function evaluations to perform this computation.
The hypervolume of the reference solution ($0.6575$) for our benchmark was
  computed by sampling the solution provided in~\cite{hbwh:05}.

@@

\lsedit{The column descriptors for the table are not clear  - better formatting needed}

@@

\subsection{AWA Photoinjector Optimization} \label{awaproblem}
Next we apply the optimization framework to a high charge beam line
 at the Argonne Wakefield Accelerator (AWA) facility. 
The goal of this optimization is to produce beams of electrons that meet 
design specifications; this includes number of particles (charge), energy, and particle distribution (characterized by beam sizes and energy spread).
As shown in Fig.~\ref{awa-linac}, the installed portion of the the 
beam line consists of an rf photocathode gun, 
two solenoids, and six linear accelerating cavities
followed by four quadrupoles and a stripline kicker. 
The charge of interest, 40 nC, is needed for Two Beam 
Acceleration (TBA) 
experiments performed at AWA \cite{gai_power_jing_2012,JING201872}, 
which motivates this work. 
Prior experimental results were limited by beam size when the beam passed through small aperture 
wakefield structures located downstream. 
In an attempt to maximize charge transmission in upcoming experiments
we optimize magnet strengths of the solenoids and quadrupoles leading into the 
TBA section of the beam line, shown in Fig.~\ref{awa-tba}.
The simulation model includes from the gun to the septum.
The optimization location is chosen as the  
entrance to the first quadrupole on the dog leg ($s_3$), see Fig.~\ref{awa-tba}.
Minimizing beam sizes here will enable capture and further focusing before space charge effects dominate the beam. 
This will also enable cleaner transport through downstream elements.
%\vspace{-1em}

@@

In addition to addressing the challenge of producing an optimized beam, 
we chose this model to demonstrate the ability of the framework to tackle large problems.
Six design variables and objectives were used, along with three constraints.
The objectives include transverse and longitudinal beam sizes, 
transverse momentum, and longitudinal energy spread. 
The design variables include the two gun solenoids and 
the first four quadrupoles settings. 
This problem encompasses high dimensionality 
and nonlinear effects such as space charge. There is no existing information
that accurately predicts optimized parameters for this beam line. 
This work is meaningful in that it will guide future operations at the AWA.

\subsubsection{Time Step Scan} \label{awa:subsection:test}
Before running a full scale optimization of the problem described in Subsection \ref{awaproblem}, 
a study on time step and number of particles in the simulation model 
was done to reduce the time of the simulation while 
maintaining the physics of interest. 
The grid size $16 \times 16 \times 32$ was chosen, 
and parallelized in the x and y directions.
After comparing several options (1,000, 10,000, 20,000, 50,000, 100,000) 
with a small time step, the number of particles was fixed at ten thousand.
Next several time steps were explored, see Table~\ref{timestep}.
The largest steps were too big to resolve the beam parameters accurately.
See low fidelity plot in Fig.~\ref{tstep} for $dT=$\num{5E-11} results.

\begin{table}%[h!]
	\begin{center}
		\caption{Checkmarks (\cmark) indicate desired beam parameters are resolved at that time step. 
			An (\xmark) indicates the time step is too large, and results are nonphysical.}
		\label{timestep}
		\begin{tabular*}{0.48\textwidth}{c @{\extracolsep{\fill}} C c D }
			\hline\noalign{\smallskip}
			Time Step (dT) & Linac & Drift & Quadrupoles \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			$5 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$5 \times10^{-11}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-11}$  & \cmark & \cmark & \xmark \\
			$5 \times10^{-12}$  & \cmark & \cmark & \xmark \\
			$1 \times10^{-12}$  & \cmark & \cmark & \cmark \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

@@

The resulting simulations are low fidelity in most places, but closely approximate 
the mid fidelity simulations for metrics of interest, as shown in 
Fig.~\ref{tstep}.  Mid fidelity simulations used steps of  $dT=\num{1E-12}$ everywhere.
The average run time of each simulation with the adjusted time steps was 1.6~minutes.
In comparison, the mid fidelity simulation ran for 18~minutes.
Note, a smaller time step, \num{1E-13}, is always used in the gun where the 
beam is low energy and changing rapidly.
%A summary of the parameters used is listed in Table \ref{fidelity}.

@@

The maximum number of individuals per generation was fixed at 80, 
Each experiment was allowed to run for twenty four hours, with 
a maximum generation limit of 100. 
We reduced the six objectives to four, 
and shortened the simulation time by moving the objectives further 
upstream to $s_1$ and $s_2$, the locations before and after the kicker.

\lsedit{Also, I had no idea what you meant by} %\text{rms}_{s}\left(s = s_1\right) until I saw the parameter list.   I would suggest`t' for time?  In any case maybe some text specifying what this is when you first mention it would be helpful.}

The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
The OPAL input file for ex-3 is given as an example to show how optimization and design variables are defined:
%

@@

After collection of the data for all four experiments, several metrics
were compared, including number of generations completed in twenty four hours and
Pareto fronts at $s_1$ and $s_2$.
From Table \ref{extable}, we clearly see ex-3 is significantly 
slower, as it evaluated only 53 generations 
compared to the experiment with the maximum number, ex-1 at 96 generations.
Perhaps this trade off would be acceptable if the Pareto front was significantly 
improved, but from Fig. \ref{expareto}, we can see this is not the case.
Similar arguments can be made for ex-2, which evaluated about 15 less generations
with no clear benefit in either Pareto front.
The Pareto fronts at $s_1$, are nearly identical. We could expect
this trend would continue given more time. 
When looking at the Pareto front at $s_2$, only ex-4 has a slight 
edge over the others.
With ex-2 and ex-3 eliminated due to evaluation time, 
and a slightly better Pareto front at $s_2$ for ex-4, the hyper parameters in ex-4 were chosen as the default values for subsequent runs.

@@

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are calculated at 
$s_3=19.4$~m, located downstream of the septum, see Fig.~\ref{awa-tba}. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24 \, \text{or} \, 25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

The first four objectives, parameters (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
at the location of interest in the beam line ($s_3$).
%Where $s_3$ is the longitudinal entrance of the fifth quadrupole. 
Minimizing the beam size at this location is essential to 
to preventing loss of particles by scraping; 
which ensures better transmission through the wakefield structures downstream. 
Less divergence in the beam (lower transverse momentum spread) 
reduces growth of transverse beam size after the focal point (location of min beam size).
This reduces halo by ensuring the beam is not over focused through a hard waist.
The momentum spread is also critical to preventing large growth during transport in bending elements. 
All of these factors help with transmission downstream.

The next two objectives in parameter (\ref{eq:awa:p4}) minimize the 
longitudinal beam size ($rms_s$), and energy spread (dE) at location $s_3$. 
This helps reduce longitudinal beam size growth in bending elements.
\lsedit{Why?  If all particles at lightspeed, then long beam size should not change in a dipole magnet}
A small bunch length ($rms_s$) is also critical to the goals of 
TBA experiments. The power generated in the wakefield structures 
designed for TBA is related to the bunch length \cite{JING201872}.
\nrnote{need better source for this info} 
i.e. smaller bunch lengths result in larger wakefields and higher power generation.

Eqs.~\ref{eq:awa:c1} to \ref{eq:awa:c3} 
define three constraints used to guide the algorithm.
The bounding values may seem large, but this is done to avoid over constraining the 
problem in early generations. When the constraints were set tighter, 
optimization runs did not reach the second generation within a 48 hour time limit. 
In other words, enough satisfactory points were not produced to fill a complete generation in 48 hours. 
By leaving the value large, a sufficient number of simulations finish
and subsequent generations are reached in a timely manner. 
As multiple generations, the objectives continue to improve.
\lsedit{the above sentence makes no sense to me}

@@

Design variables include the currents in two gun solenoids (IBF and IM), 
and four quadrupole strengths (KQ1-KQ2). The objectives include
beam size (transverse and longitudinal), transverse momentum, and energy spread as
defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
The location at the entrance of the kicker is $s_1=16.45$~meters, 
and the location of interest for objectives is $s_3=19.4$~meters. 
\lsedit{Do you mean `the objectives are optimized at location s3' in the above sentence? `location of interest for objectives' is not clear.  Also, I think your later text `This is the entrance to the fifth quad in the beam line. This location is where the beam should be captured and focused through subsequent elements.' should be moved here.}

@@

Again, the location of optimization is $s_3=19.4$ [m]. 
This is the entrance to the fifth quad in the beam line. 
This location is where the beam should be captured and focused through subsequent elements.
\lsedit{as previously mentioned, move above two sentences.}
After collection of the data, Pareto fronts comparing the objectives were plotted, 
see Figs.~\ref{fig:pareto1} and \ref{fig:pareto2}.

@@

As expected, the x dimension is impacted by the bending elements, and unable to reach 
the small beam sizes seen in the y dimension. This suggest suggests objectives in the x 
dimension will drive design variable choices used in operations. 
However, it is still necessary to 
include the y dimension in the optimization. Early optimization tests showed the y dimension 
can easily grow out of control if it is not included in the objectives.
Those results are not shown here due to the unfeasible nature of the solutions 
(i.e. $rms_y$ larger than the beam pipe).
In the case of bunch length, there are not many options to choose from.
Ignoring the extreme value on the right, Fig.~\ref{fig:pareto2} shows the 
range of optimal bunch lengths fall between 1.39 and 1.5 mm.

With these observations in mind, several beam parameters corresponding to
options on the Pareto Front in Fig.~\ref{fig:pareto1} were plotted and compared. 
A select result is shown in Fig.~\ref{fig:stat}.  \lsedit{It would be a nice addition to say which point on the pareto front that was, perhaps marking it on the curve}
The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat} (b).
The solution is nearly round, which will increase changes of keeping the beam nearly round
as it travels to the last triplet in Fig.~\ref{awa-tba}.
Overall this solution is satisfactory, and meets all requirements at the AWA.
\lsedit{Some comments on Fig. 13: FIrst, is fig 13(a) necessary?  Why can't you just add a vertical scale to fig. 13b?  Also, how about adding more info to the figure caption; is s=0 the position of the cathode?  If so, put that in the caption.  You could describe what each curve is in the figure caption for completeness.  The bottom traces show the optimized beam sizes.. The top black trace shows.. including key elements such as the kicker location.  Why do you start showing the aperture at s=10?  Is it plenty big before that?  If so, in the figure caption you could say, the aperture is shown starting at s=10 because the aperture constraints are more acute after that point.}
